M.Sc. Proposal: \\ \bigskip Computational Electrokinetics

### 2013-05-18 notes/thesis-latex-template/thesis.tex
Thanks.
Add conclusion statement.

% PhD, MSc (choose one)
% beforeExam (to make the personal thanks invisible)
\documentclass[MSc,beforeExam]{iitcsthesis}

@@

\personalThanksEnglish{Write thanks to professor and others}
\financialThanksEnglish{The generous financial support of the Technion is gratefully acknowledged.}

@@

>>>>

% PhD, MSc (choose one)
% beforeExam (to make the personal thanks invisible)
\documentclass[MSc]{iitcsthesis}

@@

\personalThanksEnglish{
\begin{center}
{\Large Acknowledgment}
\end{center}
I would like to thank my adviser, Prof. Irad Yavneh for his outstanding guidance, helpful discussions and valuable advice. 
I am deeply grateful to my family, and especially to my wife, Galit, for their love and support.
}

\financialThanksEnglish{The generous financial support of the Technion is gratefully acknowledged.}

@@

In conclusion, the main contribution of this work is the development 
of a numerical framework for solving nonlinear coupled PDE steady-state systems, 
with application to electrokinetic problems such as ion-exchanger migration and 
particle electrophoresis, and asymptotic analytical verification of the results.
